Mining Scenario/Transaction Pairs in HW/SW Co-verification Using Symbolic Execution

### 2017-04-07 paper.tex
more spelling
conclusion

\textbf{Step 3: Scenario/Transaction Pair} In \hwcbmcv, the symbolic execution 
of HW and FW models are clearly separate and the two flow meet only at the
solver phase, where a complex monolithic formula is generated in 
Conjunctive Normal Form (CNF) from the AIG and SSA.  This complex formula 
is passed on to the solver for verification purpose.  
Hence, the verification flow in \hwcbmcv limits the opportunity for extracting 
relevant scenario/transaction pairs through symbolic execution.  Instead, the 
technique relies on the underlying SAT/SMT solver to effeciently reason about 
the co-verification model. 
%
\Omit{
The hardware and firmware run independently of each other. 
The communication between them takes place through these function calls. 
}
%===============================================================================
\section{Property Specification for Co-verification}\label{property}
%===============================================================================
Lack of support for property specification in a HW/SW co-design is one of the
stumbling blocks for the application of formal techniques in co-verification.  
In this paper, we express a co-design property in C 
with the support of special primitive, called {\em next\_timeframe()}, 
that can express temporal correlation between HW and FW events. 
In this paper, we classify co-design properties into two 
classes -- {\em transaction level} property and {\em component level} property.
%-------------------------------------------------------------------------------
\subsection{Transaction level Property}
%-------------------------------------------------------------------------------
A {\em Transaction level} property ($\psi_{t}$) formally captures the 
design intent of the interaction between a $\mathcal{FT}$ and $\mathcal{HT}$, 
that is, it is defined at the transaction boundaries.  
Recall that a $\mathcal{FT}$ is a service in response to some external environment 
or HW interrupts (for example acknowledgement or exceptions). Similarly, 
$\mathcal{HT}$ is a finite-length service in response to some SW events or 
other HW events.

@@

In practice, a FW exercises only a fragment of the HW state-space for a given scenario.  
This renders many interactions between HW and FW transactions infeasible.   
Our general observation is that bounded model checking technique in \hwcbmcv 
cannot prune irrelevant transactions with respect to a given scenario, 
and hence generate a monolithic co-verification model, which are often 
extremely difficult to solve with a SAT/SMT solver. On the other hand, 
a path-based exploration strategy in \verifox is able to automatically 
mine relevant scenario/transaction pairs in a sequential co-verification 
model, owing to specific optimizations such as eager path pruning
combined with incremental SAT solving.  Our experiments show that \verifox 
is an order of magnitude faster than \hwcbmcv for proving safety as well as 
bug finding.  In the future, we plan to extend our framework to co-design 
models that exhibit further interaction patterns.

>>>>

\textbf{Step 3: Scenario/Transaction Pair} In \hwcbmcv, the symbolic execution 
of HW and FW models are clearly separate and the two flow meet only at the
solver phase, where a complex monolithic formula is generated in 
Conjunctive Normal Form (CNF) from the AIG and SSA.  This complex formula 
is passed on to the solver for verification purpose.  
Hence, the verification flow in \hwcbmcv limits the opportunity for extracting 
relevant scenario/transaction pairs through symbolic execution.  Instead, the 
technique relies on the underlying SAT/SMT solver to efficiently reason about 
the co-verification model. 
%
\Omit{
The hardware and firmware run independently of each other. 
The communication between them takes place through these function calls. 
}
%===============================================================================
\section{Property Specification for Co-verification}\label{property}
%===============================================================================
Lack of support for property specification in a HW/SW co-design is one of the
stumbling blocks for the application of formal techniques in co-verification.  
In this paper, we express a co-design property in C 
with the support of special primitive, called {\em next\_timeframe()}, 
that can express temporal correlation between HW and FW events. 
In this paper, we classify co-design properties into two 
classes -- {\em transaction level} property and {\em component level} property.
%-------------------------------------------------------------------------------
\subsection{Transaction level Property}
%-------------------------------------------------------------------------------
A {\em Transaction level} property ($\psi_{t}$) formally captures the 
design intent of the interaction between a $\mathcal{FT}$ and $\mathcal{HT}$, 
that is, it is defined at the transaction boundaries.  
Recall that a $\mathcal{FT}$ is a service in response to some external environment 
or HW interrupts (for example acknowledgement or exceptions). Similarly, 
$\mathcal{HT}$ is a finite-length service in response to some SW events or 
other HW events.

@@

In practice, a FW exercises only a fragment of the HW state-space for a given scenario.  
This renders many interactions between HW and FW transactions infeasible.   
Our general observation is that bounded model checking technique in \hwcbmcv 
cannot prune irrelevant transactions with respect to a given scenario, 
and hence generate a monolithic co-verification model, which are often 
extremely difficult to solve with a SAT/SMT solver. On the other hand, 
a path-based exploration strategy in \verifox is able to automatically 
mine relevant scenario/transaction pairs in a sequential co-verification 
model, owing to specific optimizations such as eager path pruning
combined with incremental SAT solving.  Our experiments show that \verifox 
is on average $5\times$ faster than \hwcbmcv for proving safety as well as 
bug finding.  In the future, we plan to extend our framework to co-design 
models that exhibit further interaction patterns.
